\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-04 grassposter/2015_EGU_Python/main.tex
change style for block titles, make cli listing show whole lines
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64800 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

\newcommand{\partitle}[1]{\bigskip \textbf{#1}\\[1ex]}
\newcommand{\parinlinetitle}[1]{\bigskip \textbf{#1}\ }
\newcommand{\textfontsize}{\LARGE}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Highlights}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS is a platform for geospatial computations.
\item The framework supports code maintenance which results in long term preservation of algorithms.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Description}{
% \textfontsize
\Large
\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
% \setlength{\parskip}{1em}

@@

\block{More information}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

@@

\block{GRASS Scripting library interface to GRASS GIS modules}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{PyGRASS interface to GRASS GIS modules}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using documentation for GRASS GIS modules}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\pkg{ctypes} interface to C libraries}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using NumPy}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using IPython Notebook}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Automatic creation of GUI and CLI}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{PyGRASS interface to C libraries}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Python script versus GRASS GIS module}{
and running code from IDE
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Temporal framework}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Testing the code}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{GRASS GIS Addons}{
The GRASS GIS Addons ensures long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS itself.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Alternatives to Python}{
GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
and as subprocesses virtually any language as long as proper environment is set.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Acknowledgements}{
\begin{tabular}{cp{0.75\linewidth}}
\raisebox{-.4\height}{
\includegraphics[width=0.2\linewidth]{osgeo}
}
& GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\\
\raisebox{-.8\height}{
\includegraphics[width=0.2\linewidth]{google}
}
& Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{References}{

>>>>

% License: CC0
% The license is CC0 but you can acknowledge the authors if you want to. See their names bellow.

@@

\newcommand{\partitle}[1]{\bigskip \textbf{#1}\\[1ex]}
\newcommand{\parinlinetitle}[1]{\bigskip \textbf{#1}\ }
\newcommand{\textfontsize}{\LARGE}
\newcommand{\blocktitlewrap}[1]{\textsf{\textbf{\LARGE#1}}}
% it is not possible (?) to change block title in the class, using wrapper
% the command introduced using:
%   sed -i 's/\\block{\([^}]*\)}/\\block{\\blocktitlewrap{\1}}/g' main.tex

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Highlights}}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS is a platform for geospatial computations.
\item The framework supports code maintenance which results in long term preservation of algorithms.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Description}}{
% \textfontsize
\Large
\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
% \setlength{\parskip}{1em}

@@

\block{\blocktitlewrap{More information}}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

@@

\block{\blocktitlewrap{GRASS Scripting library interface to GRASS GIS modules}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to GRASS GIS modules}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Using documentation for GRASS GIS modules}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{ctypes interface to C libraries}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Using NumPy}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Using IPython Notebook}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Automatic creation of GUI and CLI}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Python script versus GRASS GIS module}}{
and running code from IDE
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Temporal framework}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Testing the code}}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Addons}}{
The GRASS GIS Addons ensures long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS itself.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Alternatives to Python}}{
GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
and as subprocesses virtually any language as long as proper environment is set.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Acknowledgements}}{

\newcommand{\listhspace}{\hspace{0.005\linewidth}}
\newcommand{\listlogowidth}{0.22\linewidth}
\newcommand{\listtextwidth}{0.76\linewidth}

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{osgeo}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\end{minipage}

\bigskip

\begin{minipage}{\listlogowidth}
\includegraphics[width=\linewidth]{google}
\end{minipage}
\listhspace
\begin{minipage}{\listtextwidth}
Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
\end{minipage}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{References}}{
